Transition path sampling and the calculation of free energies of enzymatic reactions

### 2022-04-05 tex/manuscript.tex
added a figure and some text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Molecular dynamics (MD) simulations are increasingly being
used to calculate quantitative estimations of experimentally measurable 
kinetic and thermodynamic parameters of enzyme catalyzed reactions. 
\cite{Karplus02NatStructMolBiol9p646,
Schramm98AnnuRevBiochem67p693,Zhang05AccChemRes38p379,
Schramm11AnnuRevBiochem80p703,Schramm18ChemRev118p11194} 
This has helped in proposing mechanisms and explanations for 
enzyme activity, fast high throughput screening of thousands of inhibitor 
molecues in drug lead discovery, \cite{Jorgensen09AccChemRes42p724,Sliwoski14PharmacolRev66p334} 
directed evolution for designing enzymes with enhanced catalytic 
activities, \cite{Thyme09Nature461p1300,Bloom09PNAS106p9995,Schafer19JAmChemSoc141p10431} etc.    
Straightforward MD simulations are not employed in these cases

@@

TPS focuses on transition paths and not on stable states which introduces 
biases in the sampling of equilibrium distribution of the reaction coordinate.

@@

\item Using the shooting and shifting algorithm familiar from TPS simulations, harvest 
dynamics trajectories starting from the time slice $\tilde{z}_{j\Delta t}$ of the trajectory 

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Molecular dynamics (MD) simulations are increasingly being
used to calculate quantitative estimations of experimentally measurable 
kinetic and thermodynamic parameters of enzyme catalyzed reactions. 
\cite{Karplus02NatStructMolBiol9p646,
Schramm98AnnuRevBiochem67p693,Zhang05AccChemRes38p379,
Schramm11AnnuRevBiochem80p703,Schramm18ChemRev118p11194} 
This has helped in proposing mechanisms and explanations for 
enzyme activity, fast high throughput screening of thousands of inhibitor 
molecues in drug lead discovery, \cite{Jorgensen09AccChemRes42p724,Sliwoski14PharmacolRev66p334} 
directed evolution for designing enzymes with enhanced catalytic 
activities, \cite{Thyme09Nature461p1300,Bloom09PNAS106p9995,Schafer19JAmChemSoc141p10431} etc.    
Straightforward MD simulations are not employed in these cases because 
trajectories that take the system from reactant state to product state through
a transition state are rare and would take long time

@@

TPS focuses on transition paths and not on stable states which introduces 
biases in the sampling of equilibrium distribution of the reaction coordinate. \cite{Dellago09AdvCompSimAppp167}

@@

\item Using the shooting and shifting algorithm familiar from TPS simulations, \cite{dellago02AdvChemPhys123}
harvest dynamics trajectories starting from the time slice $\tilde{z}_{j\Delta t}$ of the trajectory 

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.9]{./figures/ada-fenergy.pdf}
\end{figure}
